### 2023-10-05 main.tex
blue

We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that

>>>>

{\color{blue}
\begin{equation}
  \mathcal{S}_{2}^{-1} |\tau\rangle= |\tau\rangle+\delta_{N,\tau}\sum_{a=1}^{N-1}\beta_a|a\rangle
\end{equation} 
\begin{equation}
  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\tau}\rangle=\left( |\tau_1\rangle+\delta_{N,\tau_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\tau_L\rangle+\delta_{N,\tau_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
\end{equation} 
\begin{equation}
  \langle \bm{\mu}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\tau}\rangle=\prod_{i=1}^L\left[ \delta_{\mu_i,\tau_i}+\delta_{N,\tau_i}\beta_{\mu_i} (1-\delta_{\mu_i,N)}\right]
\end{equation}

We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
and 
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    \end{equation}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that
